An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-26 4_method.tex
new overview figure

\section{Method}
\subsection{Overview}
The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
These offsets can be generated from the medial axis transform (MAT).
The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape. \cite{blum1967transformation}
The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}

For the uniform offsetting technique the overfill and underfill problems arise in the center,
because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.

Our framework can be thought of as following these steps:
\begin{itemize}
\item Compute the skeleton of the input shape
\item Assign each node a height in terms of bead count based on the local feature size
\item Identify central regions of the UoC
\item Quantize the height of central ridges and peaks
\item Smooth out sharp transitions between regions with different integer heights
\item Determine the heights in the periphery (non-central regions)
\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
\end{itemize}
See \cref{3d_surface_overview}.

\begin{figure*}
\centering
\setlength{\figwidth}{.18\textwidth}
\setlength{\figwidthTwo}{.17\textwidth}
\setlength{\figwidthTree}{.22\textwidth}
\setlength{\tempheight}{-0.3cm}
\setlength{\tempheightTwo}{-0.5cm}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/union_of_cones_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/uoc.pdf}
\caption{Union of Cones}\label{3d_surface_overview_uoc}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/marking_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/marked.pdf}
\caption{Center}\label{3d_surface_overview_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/rounded_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
\caption{Quantized}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figwidthTwo]{sources/method/surface/smoothed.pdf}
\caption{Smoothed}\label{3d_surface_overview_smoothed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[width=\figwidthTree]{sources/method/surface/sliced_cropped.png}

\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
\caption{Sliced}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and quantize the height in those regions \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.

For ease of reference we have included a legend explaining the vocabulary employed in this manuscript in \cref{legend}.

@@

\subsection{Surface generation}\label{sec_surface_construction}
The union of cones surface mesh can be derived from a common skeletonization of the polygonal outline shape: the medial axis.
By assigning each node in the skeleton a height equal to the radial distance to the outline we obtain the shape of the UoC.
Starting from the medial axis we further decompose the shape into simple fragments, so that the mesh contains only quads and triangles.

\subsubsection{Medial axis transform}
One of the most commonly used skeletonizations of a shape is the medial axis.
The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \cite{blum1967transformation}
We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
The resulting skeleton consists of straight edges and parabolic edges which form a graph.
See \cref{MAT_explanation_circles}.
We therefore represent the skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_datastructure}.

Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous,
or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
See \cref{MAT_explanation}.

@@

\begin{figure}
\centering
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
\caption{Circles}
\label{MAT_explanation_circles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
\caption{Wave-fronts}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
\caption{Union of Cones}
\end{subfigure}
\caption{
Medial axis representations.
The medial axis can be defined in terms of the the number of support points of the inscribed circles,
as the pinch sites in wave-fronts
or as ridges in a volume defined by the union of cones.
}
\label{MAT_explanation}
\end{figure}

>>>>

\section{Method}
\subsection{Overview}

Given an arbitrarily shaped polygon which represents the intersection of a plane and a 3D shape, our method generates a toolpath with varying width, i.e. a set of (mostly) connected line segments, with each node being assigned a width. 
The width along a line segment is linearly interpolated from the widths of its two nodes.

Our method starts with computing the skeleton of the input polygon by medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpath~\cite{eiamsa2003toward}. 
We make use of the union of cones~\cite{blum1967transformation} to visualize the skeleton, by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (Fig. 2?).
With the aid of this visualization, contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (Fig. 2?).

As depicted in Fig. 2?-?, starting from the medial axis, our method first identifies edges and nodes in the skeleton that are located in the central of the polygon. The heights at these elements (the distance of the corresponding projected point to the polygon boundary) are then quantized in terms of the number of beads. To ensure a smooth toolpath between regions with quantized integer heights that different more than two, we add new nodes in the skeleton and assign them interpolated integer heights. The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain a toolpath with varying width.
\jun{Do we use regular intervals, but get varying width?}

We note that the union of cones (or UoC) is introduced only for visualization. We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.

This section explains how we can generate toolpaths with evenly distributed bead widths. In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.

% The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
% These offsets can be generated from the medial axis transform (MAT).
% The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape. \cite{blum1967transformation}
% The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
% We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}

% For the uniform offsetting technique the overfill and underfill problems arise in the center,
% because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
% Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.

% Our framework can be thought of as following these steps:
% \begin{itemize}
% \item Compute the skeleton of the input shape
% \item Assign each node a height in terms of bead count based on the local feature size
% \item Identify central regions of the UoC
% \item Quantize the height of central ridges and peaks
% \item Smooth out sharp transitions between regions with different integer heights
% \item Determine the heights in the periphery (non-central regions)
% \item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
% \end{itemize}
% See \cref{3d_surface_overview}.

\begin{figure*}
\centering
\setlength{\figheight}{.15\textwidth}
\setlength{\figwidth}{.15\textwidth}
\setlength{\figwidthTwo}{.22\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
\caption{Layer outline}\label{}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
\caption{Skeleton}\label{}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
\caption{Union of Cones}\label{}
\end{subfigure}
\begin{subfigure}{\figwidthTwo}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
\caption{Slicing}\label{}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
\caption{Uniform paths}\label{}
\end{subfigure}

\setlength{\figwidth}{.22\textwidth}
\setlength{\figwidthTwo}{.17\textwidth}
\setlength{\figwidthTree}{.22\textwidth}
\setlength{\tempheight}{-0.3cm}
\setlength{\tempheightTwo}{-0.5cm}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/marking_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/marked.pdf}
\caption{Center identification}\label{3d_surface_overview_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/rounded_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/rounded.pdf}
\caption{Quantization}\label{3d_surface_overview_rounded}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/smoothed.pdf}
\caption{Smoothing}\label{3d_surface_overview_smoothed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\hspace*{\tempheightTwo}
\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_cropped.png}

@@

\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
\end{subfigure}
\caption{
A geometrical conceptualization of our technique.
3D visualization on top and the corresponding 2D visualization on bottom.
In the UoC \subref{3d_surface_overview_uoc}
we mark the central regions \subref{3d_surface_overview_center}
and quantize the height in those regions \subref{3d_surface_overview_rounded}.
We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
Blue signifies regions marked as being central.
The numbers are the integer multiples of half the nozzle width.
}
\label{3d_surface_overview}
\end{figure*}

For ease of reference we have included a legend explaining \jun{this figure itself does not sufficiently "explain". How about indicating, highlighting etc?} the terms employed in this manuscript in \cref{legend}.
These terms will be further explained as they first appear later in the paper.

@@

\subsection{Surface generation}\label{sec_surface_construction}
\jun{I would like to change the title, don't have a better word.}

The union of cones surface mesh can be derived from a common skeletonization of the polygonal outline shape: the medial axis.
By assigning each node in the skeleton a height equal to the radial distance to the outline we obtain the shape of the UoC.
Starting from the medial axis we further decompose the shape into simple fragments, so that the mesh contains only quads and triangles.

\subsubsection{Medial axis transform}
The medial axis is a compact and intrinsic representation of shapes.
It is defined by the locations where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation}.
We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}:
\begin{equation}
    \text{sup}(v) = \argmin_{x\in P} |x - v|.
\end{equation}
The resulting skeleton consists of straight edges and parabolic edges which form a graph.
See \cref{MAT_explanation_circles}.
%We therefore represent the skeleton in a standard half-edge data-structure.
%See \cref{shape_decomposition_datastructure}.

%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
%This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
%The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
%See \cref{MAT_explanation}.

@@

% \begin{figure}
% \centering
% \begin{subfigure}{0.3\columnwidth}
% \centering
% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
% \caption{Circles}
% \label{MAT_explanation_circles}
% \end{subfigure}
% \begin{subfigure}{0.3\columnwidth}
% \centering
% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
% \caption{Wave-fronts}
% \end{subfigure}
% \begin{subfigure}{0.3\columnwidth}
% \centering
% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
% \caption{Union of Cones}
% \end{subfigure}
% \caption{
% Medial axis representations.
% The medial axis can be defined in terms of the the number of support points of the inscribed circles,
% as the pinch sites in wave-fronts
% or as ridges in a volume defined by the union of cones.
% }
% \label{MAT_explanation}
% \end{figure}
